### 2021-04-02 Main_Figures/Global_trait_spectrum.Rmd
Organizing folders and script with all the analysis

#Load data
dat_cleaning_5 <- readRDS("Data/RData/data_all_species_for_rmd_plot_ppca_CLUSTERS.rds")
phyl_pca_forest <- readRDS("Data/RData/phyl_pca_forest.rds")

@@

  plot <- plot+stat_density2d(aes(fill=..level..,alpha=..level..),geom='polygon') + 
  scale_fill_continuous(low="green",high="red",guide=FALSE,breaks = c(0.025, 0.050, 0.075), labels = c("Low", "Medium", "High")) + theme(legend.position = "none")+guides(fill = guide_legend(override.aes = list(alpha = 0.85),title="Kernel density"))+
    scale_alpha(guide = 'none')

@@

  plot <- plot + theme_bw() + annotation_raster(tree_1, xmin = -4, xmax = -2.9,ymin = 2.45, ymax = 4.35)+
     annotation_raster(style_l_1, xmin = 2.45, xmax = 3.25,ymin = 2.25, ymax = 3.35) +
    annotation_raster(style_s_1, xmin = -3.25, xmax = -2.45,ymin = -2.65, ymax = -1.75) +
    annotation_raster(ovule_h_1, xmin = 3.5, xmax = 4.15,ymin = -0.65, ymax = 0.25) +
    annotation_raster(ovule_l_1, xmin = -4.1, xmax = -3.5,ymin = -0.3, ymax = 0.6) +
    annotation_raster(selfing_n_1, xmin = -0.2, xmax = 1.2,ymin = 2.8, ymax = 4.7) +
    annotation_raster(selfing_h_1, xmin = -0.95, xmax = 0,ymin = -4.1, ymax = -3.25) +
    annotation_raster(single_flower_1, xmin = 3.0, xmax = 3.7,ymin = -2, ymax = -1.1) +
    annotation_raster(many_flowers_1, xmin = -4.60, xmax = -3.15,ymin = 1, ymax = 2.15) +
    annotation_raster(large_flower_1, xmin = 3.4, xmax = 4.2,ymin = 1, ymax = 2.1) +
    annotation_raster(flower_small_1, xmin = -4, xmax = -1.85,ymin = -2.4, ymax = -0.4) +
    annotation_raster(single_flower_1, xmin = 2.8, xmax = 3.5,ymin = -3, ymax = -2.2)

@@

  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
 plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,5.5,5.5,7.5,7.3,6)), y = -(PCAloadings$PC2*c(4.77,2.4,3,6.5,14,5.5)),
                         label = PCAloadings$Variables, color="black",fontface =2,size=5)

>>>>

#Load data
dat_cleaning_5 <- readRDS("Data/RData/data_all_species_PPCA.rds")
phyl_pca_forest <- readRDS("Data/RData/phyl_pca_forest.rds")

@@

  plot <- plot+stat_density2d(aes(fill=..level..,alpha=..level..),geom='polygon') + 
  scale_fill_continuous(low="green",high="red",guide=FALSE,breaks = c(0.02, 0.050, 0.09), labels = c("Low", "Medium", "High")) + theme(legend.position = "none")+guides(fill = guide_legend(override.aes = list(alpha = 0.7),title="Kernel density"))+
    scale_alpha(guide = 'none')

@@

  plot <- plot + theme_bw() + annotation_raster(tree_1, xmin = -4, xmax = -2.9,ymin = 2.45, ymax = 4.35)+
     annotation_raster(style_l_1, xmin = 2.45, xmax = 3.25,ymin = 2.25, ymax = 3.35) +
    annotation_raster(style_s_1, xmin = -3.05, xmax = -2.25,ymin = -2.65, ymax = -1.75) +
    annotation_raster(ovule_h_1, xmin = 3.5, xmax = 4.2,ymin = -0.45, ymax = 0.50) +
    annotation_raster(ovule_l_1, xmin = -4.2, xmax = -3.5,ymin = -0.45, ymax = 0.5) +
    annotation_raster(selfing_n_1, xmin = -0.2, xmax = 1.2,ymin = 2.8, ymax = 4.7) +
    annotation_raster(selfing_h_1, xmin = -0.95, xmax = 0,ymin = -4.1, ymax = -3.25) +
    annotation_raster(single_flower_1, xmin = 3.3, xmax = 4.1,ymin = -1.7, ymax = -0.7) +
    annotation_raster(many_flowers_1, xmin = -4.60, xmax = -3.15,ymin = 1, ymax = 2.15) +
    annotation_raster(large_flower_1, xmin = 3.4, xmax = 4.2,ymin = 1, ymax = 2.1) +
    annotation_raster(flower_small_1, xmin = -4, xmax = -1.85,ymin = -2.4, ymax = -0.4) +
    annotation_raster(single_flower_1, xmin = 2.8, xmax = 3.5,ymin = -2.8, ymax = -2.2)

@@

  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
 plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,5.5,5.5,7.5,7.3,6)), y = -(PCAloadings$PC2*c(4.77,2.4,3,6.5,5,5.5)),
                         label = PCAloadings$Variables, color="black",fontface =2,size=5)
